Compositional Certified Resource Bounds

### 2015-04-15 paper/main.tex
add the DOI number, add notes in Table 3 caption

\conferenceinfo{PLDI'15}{June 13--17, 2015, Portland, OR, USA}
\copyrightyear{2015}
\copyrightdata{978-1-4503-3468-6/15/06}
\doi{nnnnnnn.nnnnnnn}

@@

\pref{tab:compar} summarizes the results of our experiments presented
in \pref{tab:eval}.  It shows
for each tool the number of derived bounds (\#bounds), the number of
asymptotically tight bounds (\#lin. bounds), the number of bounds with
the best constant factors in comparison with the other tools (\#best
bounds), and the number of examples that we were able to test with the
tool (\#tested).  Since we were not able to run the experiments for KoAT
and SPEED, we simply used the bounds that have been reported by the
authors of the respective tools.  The results show that our automatic
amortized analysis outperforms the existing tools on our example
programs.  However, this experimental evaluation has to be taken with
a grain of salt.  Existing tools complement $\toolname$
since they can derive polynomial bounds and support
more features of C.  We were particularly impressed by LOOPUS which is
very robust, works on large C files, and derives very precise bounds.
\iffull{We did not include the running times of the tools in the table since
all tested tools work very efficiently and need less then a second
on every tested example.}{}

@@

\begin{table*}[h!]
\appendix
\section{Complete Experimental Results for the Tool Comparison}

\renewcommand{\max}[0]{{\rm mx}}
\nocaptionrule \caption{
  Comparison of the bounds generated by KoAT, Rank,
  LOOPUS, SPEED, and our tool $\toolname$ on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications~\cite{GulwaniJK09,GulwaniMC09,GulwaniZ10,SinnZV14} because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize

>>>>

\conferenceinfo{PLDI'15}{June 13--17, 2015, Portland, OR, USA}
\copyrightyear{2015}
\copyrightdata{978-1-4503-3468-6/15/06}
\doi{2737924.2737955}

@@

\pref{tab:compar} summarizes the results of our experiments presented
in \pref{app:eval}.  It shows
for each tool the number of derived bounds (\#bounds), the number of
asymptotically tight bounds (\#lin. bounds), the number of bounds with
the best constant factors in comparison with the other tools (\#best
bounds), and the number of examples that we were able to test with the
tool (\#tested).  Since we were not able to run the experiments for KoAT
and SPEED, we simply used the bounds that have been reported by the
authors of the respective tools.  The results show that our automatic
amortized analysis outperforms the existing tools on our example
programs.  However, this experimental evaluation has to be taken with
a grain of salt.  Existing tools complement $\toolname$
since they can derive polynomial bounds and support
more features of C.  We were particularly impressed by LOOPUS which is
very robust, works on large C files, and derives very precise bounds.
\iffull{We did not include the running times of the tools in the table since
all tested tools work very efficiently and need less then a second
on every tested example.}{}

@@

\begin{table*}[h!]
\appendix
\section{Complete Experimental Results for the Tool Comparison}
\label{app:eval}

\renewcommand{\max}[0]{{\rm mx}}
\nocaptionrule \caption{
  Comparison of the bounds generated by KoAT, Rank,
  LOOPUS, SPEED, and our tool $\toolname$ on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications~\cite{GulwaniJK09,GulwaniMC09,GulwaniZ10,SinnZV14} because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.  Functions with names of the form \code{tXX} are complex tests
  that we designed during the development of $\toolname$.  The source code for all the functions
  is available in the extended version~\cite{anon_extended}.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize
